### 2014-03-15 docs/paper.tex
Split Telex, better CensorSpoofer.

Decoy routing is
a recently proposed anti-blocking approach. Telex~\cite{telex}
asks friendly ISPs to deploy special software on routers between censored users and
popular, uncensored Internet destinations.
Circumvention traffic is marked with a special ``tag'' that is distinguishable from a random string only
by Telex routers (not by the censor).
On receiving such a tagged communication, the Telex router shunts it away from its apparent destination
and toward the censored destination requested by the client.
CensorSpoofer~\cite{censorspoofer}
decouples the upstream and downstream channels.
Upstream data are carried over a low-bandwidth covert channel such as email.
The CensorSpoofer proxy protects its address by
spoofing the source IP address of all downstream data sent back to the client.
In addition to spoofing, the CensorSpoofer authors propose to obfuscate the downstream with a SIP-based steganographic channel.
A recent study~\cite{nodirectionhome} on AS
topology suggests that defeating decoy routing is likely to be expensive for the
censors, if the decoy routers are strategically deployed. Despite that decoy
routing is a sound technical approach, it is still questionable whether ISPs are
willing to act against state-level censors. However, the takeaway is that the
censors are unwilling to completely block day-to-day Internet access, which we
can take advantage of.
Of the decoy routing systems, Telex is the most similar to our work.
Both systems use a piece of network infrastructure as a decoy to redirect certain flows
(for Telex it is an ISP router; for us it is the Google frontend server),
and both tag flows in a way that is visible only to the decoy router
(for Telex a tag is a hash embedded in the TLS client randomness; for us it is the HTTP Host header).

% Routing around decoys
% Cirripede

>>>>

Decoy routing is
a recently proposed anti-blocking approach. Telex~\cite{telex}
asks friendly ISPs to deploy special software on routers between censored users and
popular, uncensored Internet destinations.
Circumvention traffic is marked with a special ``tag'' that is distinguishable from a random string only
by Telex routers (not by the censor).
On receiving such a tagged communication, the Telex router shunts it away from its apparent destination
and toward the censored destination requested by the client.
Telex is conceptually similar to our work.
Both systems use a piece of network infrastructure as a decoy to redirect certain flows
(for Telex it is an ISP router; for us it is the Google frontend server),
and both tag flows in a way that is visible only to the decoy router
(for Telex a tag is a hash embedded in the TLS client randomness;
for us it is the HTTP Host header, hidden within an HTTPS stream).
An important difference is that Telex requires some degree of buy-in from network operators
whose incentives may not be aligned with circumventors'.
We require no active participation on the part of the frontend operator,
only a lack of active opposition.

CensorSpoofer~\cite{censorspoofer}
decouples the upstream and downstream channels.
The client sends upstream data to the CensorSpoofer proxy over a low-bandwidth covert channel such as email.
At the same time, the client pretends to have an innocuous communication (such as a VoIP call) with an unblocked dummy host.
The CensorSpoofer proxy sends encrypted UDP data back downstream to the client,
protecting its true IP address by spoofing the source of all its packets
so that they appear to come from the dummy host.
From the censor's point of view, the client is carrying on a conversation only with the dummy host.
If the dummy is blocked, another can be used in its place,
as the CensorSpoofer proxy's true IP address remains unknown.
% Cirripede

% Routing around decoys
A recent study~\cite{nodirectionhome} on AS
topology suggests that defeating decoy routing is likely to be expensive for the
censors, if the decoy routers are strategically deployed. Despite that decoy
routing is a sound technical approach, it is still questionable whether ISPs are
willing to act against state-level censors. However, the takeaway is that the
censors are unwilling to completely block day-to-day Internet access, which we
can take advantage of.
